Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-03-05 papers/eccv2018/3_evaluation.tex
papers: added changes to evaluation, results and conclusions

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}. The mushroom body in this species is the primary site of associative learning. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $1000 \times 1000 \times 1000$ voxels.

@@

The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. Ideally, the merge candidates output by this algorithm will contain all possible positive examples with a very limited number of negative examples. After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{600}{\nano\meter}$ produce the best results considering this objective.

@@

%Table \ref{table:skeletonization} shows the overall success of our graph creation method with candidate pruning. \hp{not clear what this table is showing--explain. put this in the experiment section where you discuss the results}

@@

We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. The supplemental material includes information on the experiments that determined these final parameters. Table~\ref{table:architecture} provides the parameters of the final network. 
There are 7,294,705 learnable parameters in our final architecture. 
All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
Training concluded after \TODO{YYY} epochs.

\begin{table}[h!]
	\centering
	\begin{tabular}{l l} \hline
		\textbf{Parameters} & \textbf{Values} \\ \hline
		Loss Function & Mean Squared Error \\
		Optimizer & SGD  with Nesterov Momentum \\
		Momentum & 0.9 \\
		Initial Learning Rate & 0.01 \\
		Decay Rate & $5 * 10^{-8}$ \\
		Activation & LeakyReLU $(\alpha = 0.001)$ \\
		Kernel Sizes & $3 \times 3 \times 3$ \\
		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
	\end{tabular}
	\caption{Training parameters.}
	\label{table:architecture}
\end{table}

@@

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive and \TODO{7000} negative examples.
To avoid overfitting our deep networks, we apply the following augmentations on the example.
During a single batch, we randomly select ten positive examples and ten negative examples. 
With probability 0.5, the example is flipped across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating that benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

%\subsection{Graph-based Strategies}

%Applying a top-down globally optimal partitioning function allows us to enforce some domain-specific constraints on the reconstruction.
%In connectomics, we want to enforce the topological restrictions that each partition in the graph has a genus of zero.
%The greedy-additive heuristic solves the multicut graph partitioning problem by enforcing this constraint.
%Previous agglomeration strategies at the per-region level consider neighboring superpixels in order of merge probability.
%These superpixels are clustered hierarchically without concern for global constraints.
%We compare the benefits of a top-down partitioning function versus the traditional bottom-up clustering methods.

>>>>

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The mushroom body in this species is the primary site of associative learning. 
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.

@@

The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segments pairs. 
After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{400}{\nano\meter}$ produce reasonable results on our training data considering this objective.

@@

@@

We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
The supplemental material includes information on the experiments that determined these final parameters. 
Table~\ref{table:architecture} provides the parameters of the final network. 
There are \TODO{X,XXX,XXX} learnable parameters in our final architecture. 
All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
Training concluded after \TODO{XXX} epochs.

\begin{table}[h!]
	\centering
	\begin{tabular}{l l} \hline
		\textbf{Parameters} & \textbf{Values} \\ \hline
		Loss Function & Mean Squared Error \\
		Optimizer & SGD  with Nesterov Momentum \\
		Momentum & 0.9 \\
		Initial Learning Rate & 0.0001 \\
		Decay Rate & $5 * 10^{-8}$ \\
		Activation & LeakyReLU $(\alpha = 0.001)$ \\
		Kernel Sizes & $3 \times 3 \times 3$ \\
		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
	\end{tabular}
	\caption{Training parameters.}
	\label{table:architecture}
\end{table}

@@

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive merge examples and \TODO{7000} negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating that benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

### 2018-03-05 papers/eccv2018/4_results.tex
paper: major changes to abstract, intro, and related works
papers: added changes to evaluation, results and conclusions

%\section{Results}

@@

We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropies between two clusterings, lower VI scores are better.

@@

Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by 19.3\% on the three testing datasets. 
Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see significant improvements on the Kasthuri datasets (VI split reduction of 27.7\% and 24.8\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of 15.2\% and 18.0\%). This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.

@@

Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. The baseline algorithm considers all adjacent regions for merging. Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 753 compared to 763). Our pruning heuristic removes at least $6\times$ the number of edges on all datasets, achieving a maximum removal rate of $20\times$.

@@

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:positive-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
This is a large benefit over enforcing segment adjacency.

There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons. 
Fig.~\ref{fig:skeleton-results} shows such a case. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
	\caption{A false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
	\label{fig:skeleton-results}
\end{figure}

@@

When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Table ~\ref{table:inference-augmentation}). 
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

\TODO{Add table for augmentation}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{./figures/receiver-operating-characteristic.jpg}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume. The dashed blue line indicates better performance on the FlyEM datasets with retraining compared to without (solid blue).}
	\label{fig:receiver-operating-characteristic}
\end{figure}

@@

The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by 36.1\%, 12.2\%, and 13.6\%, respectively.

>>>>

@@

We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. 
Since we are measuring the entropy between two clusterings, lower VI scores are better.

@@

Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \TODO{XX}\% on the three testing datasets. 
Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\% and \TODO{XX}\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \TODO{XX}\% and \TODO{XX}\%). 
This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. 
Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.

@@

Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
We present additional analysis of the skeletonization parameters in the supplemental material.

@@

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
This is a large benefit over enforcing segment adjacency.

There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results} shows two such cases. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average $\TODO{XX}$ such examples in our datasets, corresponding to $\TODO{XX}$ in the variation of information split score.

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}
	\caption{Two false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate. \TODO{SECOND EXAMPLE}}
	\label{fig:skeleton-results}
\end{figure}

@@

Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Table ~\ref{table:inference-augmentation}). 
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

\begin{table}
	\begin{center}
		\begin{tabular}{c | c c c}
			Dataset & Precision & Recall & Accuracy \\ \hline
			Kasthuri & & & \\
			FlyEM Vol. 1 & & & \\
			FlyEM Vol. 2 & & & 
		\end{tabular}
		\caption{Data augmentation during test time increases the precision, recall, and accuracy of all three datasets.}
		\label{table:inference-augmentation}
	\end{center}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.jpg}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume. The dashed blue line indicates better performance on the FlyEM datasets with retraining compared to without (solid blue).}
	\label{fig:receiver-operating-characteristic}
\end{figure}

@@

The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.

### 2018-03-05 papers/eccv2018/5_conclusions.tex
updated paper to eccv format
papers: added changes to evaluation, results and conclusions

There is significant room for additional research and improvements. We can augment the graph with additional information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc. This would allow us to enforce additional biological constraints during graph partitioning. For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections. An augmented graph would also be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. Finally, we believe that the benefits of top-down enhancements from graph optimization can extend beyond connectomics to other domains, such as medical image segmentation.

>>>>

In the future, these methods can be adjusted to apply more specific domain constraints. 
We can augment the graph with additional information from the image data, such as synaptic locations, cell morphology, locations of mitochondria, etc. 
This would allow us to enforce more biological constraints during graph partitioning. 
For example, we could then enforce the constraint that a given segment only has post- or pre-synaptic connections. 
An augmented graph would also be helpful for splitting improperly merged segments by adding additional terms to the partitioning cost function. 
Finally, we believe that the benefits of top-down enhancements from graph optimization can extend beyond connectomics to other domains, such as medical image segmentation.
